---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 300,
  dev.args = list(png = list(type = "cairo"))
)
```

# plottwist2

<!-- badges: start -->
<!-- badges: end -->

plottwist2 contains several functions to speed up the creation of neat plots with ggplot2 and expand functionality. In particular, `geom_symbol()` and `geom_pattern()` are intended to reduce reliance on colour for distinguishing between groups, by adding a wider variety of point shapes and bar textures respectively.

## Installation

You can install the development version of plottwist2 from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("joepennycook/plottwist2")
```

## Example

`geom_symbol()` allows simple point shapes alongside more complex options.

```{r example}
library(ggplot2)
library(plottwist2)

ggplot(data = iris, aes(x = Sepal.Length, y = Petal.Length)) +
  geom_symbol(aes(symbol = Species)) +
  scale_symbol_manual(values = c(12, 20, 28)) +
  theme_simple()
```
